---
title: "Presentation with RevealJS"
format: revealjs
author: "Bella"
---

## Hands-on: Tinkering with RevealJS

### Instructions:

1.  Amend the YAML Header to make slides incremental
2.  Add new slides
3.  Edit the code chunks to appear on the slides

## The Diamonds dataset

```{r}
#| echo: true
library(tidyverse)
library(corrplot)
library(gtsummary)
```

The dataset, available through `ggplot2` package, contains the prices and other attributes of over 50,000 round cut diamonds, specifically 53,940 diamonds. It includes various details such as the price, weight, cut quality, color, clarity, and dimensions of the diamonds. Below is a table detailing the variables included in the dataset:

| **Variable** | **Description**                                                                                   |
|--------------|----------------------------------------------------------|
| price        | Price in US dollars (\$326–\$18,823)                                                              |
| carat        | Weight of the diamond (0.2–5.01)                                                                  |
| cut          | Quality of the cut (Fair, Good, Very Good, Premium, Ideal)                                        |
| color        | Diamond color, from D (best) to J (worst)                                                         |
| clarity      | A measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best)) |
| x            | Length in mm (0–10.74)                                                                            |
| y            | Width in mm (0–58.9)                                                                              |
| z            | Depth in mm (0–31.8)                                                                              |
| depth        | Total depth percentage = z / mean(x, y) = 2 \* z / (x + y) (43–79)                                |
| table        | Width of top of diamond relative to widest point (43–95)                                          |

## Diamonds overview

```{r}
head(diamonds)
```

## Descriptive statistics for numeric variables

mean, median, and standard deviation for `price` and `carat`:

```{r}
diamonds %>% 
  tbl_summary(
    include = c(price, carat, x, y, depth, table),
    by = cut
  ) %>% 
    add_n()

```

## Histogram of Diamond prices

```{r}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(binwidth = 500, fill = "blue", color = "black") +
  labs(title = "Histogram of Diamond Prices", x = "Price (USD)", y = "Frequency")
```

## Distribution of prices for each cut category

```{r}
ggplot(diamonds, aes(x = cut, y = price)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Boxplot of Diamond Price by Cut", x = "Cut", y = "Price (USD)")
```

## Correlations {background-color="black"}

Correlation matrix for numeric variables:

```{r}
numeric_vars <- diamonds %>% select(price, carat, x, y, z, depth, table)
cor_matrix <- cor(numeric_vars)

corrplot(cor_matrix, method = "circle")
```

## Simple Regression 

Does a diamond's carat affect its price?

```{r}
model_price <- lm(price ~ carat + depth, data = diamonds)

table_carat <- tbl_regression(model_price)
table_carat
```
